# Load all the necessary libraries

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
```

# Add the data

```{r}
install.packages(mosaicData)
library(mosaicData) 
data(Gestation)
```

# Cleaning the data

This section included the filtration of the data to remove NA values and selection of the columns from the data set that will be used in the hypotheses

```{r}
Gestation_edits <- select(Gestation, gestation, age, parity, dht, wt) %>%
  filter(
    !is.na(age),
    !is.na(gestation),
    !is.na(parity),
    !is.na(dht),
    !is.na(wt),
  )
```

# Introduction of Data

words about the data go here!

# Hypotheses

## Hypothesis 1:

H1: The `age` of the mother impacts the `gestation` period.\
H0: The `age` of the mother does not impact the `gestation` period.

## Hypothesis 2:

H2: Smoking status "`smoke`" impacts the `gestation` period.\
H0: Smoking status "`smoke`" does not impact the `gestation` period.

## Hypothesis 3:

H3: `Gestation` period impacts birth weight "`wt`".\
H0: `Gestation` period does not impact birth weight "`wt`".

# Visualizations

## Visualization 1 - Maternal Age vs Gestation Period

```{r}
ggplot(Gestation_edits, aes(x = age, y = gestation)) + 
  geom_point() +
  labs(
    title = "Maternal Age vs Gestation",
    x = "Maternal Age (years)",
    y = "Gestation Period (days)"
  ) +
  theme_classic(
  )
```

## Visualization 2 - Smoking Status vs Gestation Period

```{r}
ggplot(Gestation_edits, aes(x = smoke, y = gestation)) + 
  geom_boxplot() +
  labs(
    title = "Gestation Period vs Smoking Status",
    x = "Smoking Status",
    y = "Gestation period (days)"
  ) +
  theme_classic(
  )
```

## Visualization 3 - Gestation Period vs Birth Weight

```{r}
ggplot(Gestation_edits, aes(x = gestation, y = wt)) + 
  geom_point() +
  labs(
    title = "Gestation Period vs Birth Weight",
    x = "Gestation Period (days)",
    y = "Birth Weight (oz)"
  ) +
  theme_classic(
  )
```

# Fitting the Model

```{r}
gestation_lm <- lm(gestation ~ wt + smoke + age, data = Gestation_edits)
summary(gestation_lm)
autoplot(gestation_lm)
```

# Improving the Model

##Log
Gestation$logexp <- log(Gestation$gestation)
Gestation_log_lm <- lm(logexp ~ age + wt + smoke, data = Gestation)

autoplot(Gestation_log_lm)

##Sqrt
Gestation_edits$sqrt_gestation <- sqrt(Gestation_edits$gestation)

# Fit the model with square root transformed gestation
gestation_lm_sqrt <- lm(sqrt_gestation ~ wt + smoke + age, data = Gestation_edits)
summary(gestation_lm_sqrt)

autoplot(gestation_lm_sqrt)

##ELP- trying to take the upper and lower and fiting the model but i keep getting error

# Testing Your Hypotheses

## Hypothesis 1:

H1: The `age` of the mother impacts the `gestation` period.\
H0: The `age` of the mother does not impact the `gestation` period.

## Hypothesis 2:

H2: Smoking status "`smoke`" impacts the `gestation` period.\
H0: Smoking status "`smoke`" does not impact the `gestation` period.

## Hypothesis 3:

H3: `Gestation` period impacts birth weight "`wt`".\
H0: `Gestation` period does not impact birth weight "`wt`".

## Hypothesis 1

# Fit the model
model_age <- lm(gestation ~ age, data = Gestation_edits)

# Summary of the model
summary(model_age)

# ANOVA test
anova(model_age)

# Drop1 test
drop1(model_age, test = "F")

## Hypothesis 2

# Fit the model
model_smoke <- lm(gestation ~ smoke, data = Gestation_edits)

# Summary of the model
summary(model_smoke)

# ANOVA test
anova(model_smoke)

# Drop1 test
drop1(model_smoke, test = "F")

## Hypothesis 3

# Fit the model
model_wt <- lm(gestation ~ wt, data = Gestation_edits)

# Summary of the model
summary(model_wt)

# ANOVA test
anova(model_wt)

# Drop1 test
drop1(model_wt, test = "F")

# Assessing Conclusions

#Revisit autoplot:

#Check for influential points:
# Load necessary library
library(ggfortify)

# Fit the model
model <- lm(gestation ~ wt + smoke + age, data = Gestation_edits)

# Diagnostic plots
autoplot(model)

# Identify influential points
influential_points <- which(cooks.distance(model) > (4 / nrow(Gestation_edits)))

# Remove influential points
Gestation_no_influential <- Gestation_edits[-influential_points, ]

# Refit the model without influential points
model_no_influential <- lm(gestation ~ wt + smoke + age, data = Gestation_no_influential)
summary(model_no_influential)

autoplot(model_no_influential)

#Issues with multicollinearity? IDK Queen
# Load necessary library
library(car)

# Compute VIF
vif(model)

# Automatic Model Selection

# Conclusions
