# Load all the necessary libraries

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
```

# Add the data

```{r}
install.packages(mosaicData)
library(mosaicData) 
data(Gestation)
```

# Cleaning the data

This section included the filtration of the data to remove NA values and selection of the columns from the data set that will be used in the hypotheses

```{r}
Gestation_edits <- select(Gestation, gestation, age, parity, dht, wt) %>%
  filter(
    !is.na(age),
    !is.na(gestation),
    !is.na(parity),
    !is.na(dht),
    !is.na(wt),
  )
```

# Introduction of Data

words about the data go here!

# Hypotheses

## Hypothesis 1:

H1: The `age` of the mother impacts the `gestation` period.\
H0: The `age` of the mother does not impact the `gestation` period.

## Hypothesis 2:

H2: Smoking status "`smoke`" impacts the `gestation` period.\
H0: Smoking status "`smoke`" does not impact the `gestation` period.

## Hypothesis 3:

H3: `Gestation` period impacts birth weight "`wt`".\
H0: `Gestation` period does not impact birth weight "`wt`".

# Visualizations

## Visualization 1 - Maternal Age vs Gestation Period

```{r}
ggplot(Gestation_edits, aes(x = age, y = gestation)) + 
  geom_point() +
  labs(
    title = "Maternal Age vs Gestation",
    x = "Maternal Age (years)",
    y = "Gestation Period (days)"
  ) +
  theme_classic(
  )
```

## Visualization 2 - Smoking Status vs Gestation Period

```{r}
ggplot(Gestation_edits, aes(x = smoke, y = gestation)) + 
  geom_boxplot() +
  labs(
    title = "Gestation Period vs Smoking Status",
    x = "Smoking Status",
    y = "Gestation period (days)"
  ) +
  theme_classic(
  )
```

## Visualization 3 - Gestation Period vs Birth Weight

```{r}
ggplot(Gestation_edits, aes(x = gestation, y = wt)) + 
  geom_point() +
  labs(
    title = "Gestation Period vs Birth Weight",
    x = "Gestation Period (days)",
    y = "Birth Weight (oz)"
  ) +
  theme_classic(
  )
```

# Fitting the Model

```{r}
gestation_lm <- lm(gestation ~ wt + smoke + age, data = Gestation)
summary(gestation_lm)
```

# Improving the Model

# Testing Your Hypotheses

# Assessing Conclusions

# Automatic Model Selection

# Conclusions
